Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-06-01 paper/HH4b.tex
changed front page
Some work on the draft

\title{Boosting Higgs Pair Production in the $4b$ Channel at the LHC with Multivariate Techniques}

@@

\emailAdd{juan.rojo@physics.ox.ac.uk}

@@

\abstract{
A nice abstract
}

>>>>

\title{Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques}

@@

\emailAdd{cigdem.issever@physics.ox.ac.uk}

@@

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the full electroweak
  symmetry breaking potential, in particular to the Higgs trilinear coupling.
  %
  In this work we study the feasibility of measuring the production of
  Higgs boson pairs at the High-Luminosity LHC using the
  $bb\bar{b}\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs to
  $b\bar{b}$ pairs, this measurement is extremely challenging due to the
  overwhelming QCD background.
  %
  By combining the cintribution from resolved, boosted and intermediate
  topologies, and enhancing the signal over background ratio
  using multivariaty techniques, we find that a significance of AAA
  can be obtained at 14 TeV with 3000 fb$^{-1}$.
}
